---
title: "Diagnostics for Linear Regression"
author: "Nick"
---


In this document we will be looking at a few ways to analyze the model that we've come up with in order to see if the model we've generated is a "good" model.

---
```{r}
## load the data
multi = read.table("multi.txt", header = TRUE)
mod1 = lm(Y ~ X3 + X2 + X4 , data = multi)
y = multi[,1]
x2 = multi[,3]
x3 = multi[,4]
x4 = multi[,5]
par(mfrow=c(1,3))

plot(x3,y, data = multi)
plot(x2,y, data = multi)

plot(x4,y, data = multi)
cor(multi, method = "pearson")
```
---
We can see the linear relationship between y and the predictors in the model. We can also use Pearsons correlation to find the relationship between each predictor and Y in the first column.
---
In order to check to see if the assumptions of linear regression are satisfied we must run some diagnostic tests to see which, if any, of our assumptions have been violated.
---
```{r}
par(mfrow=c(2,2))
x3 = multi[,4]
x2 = multi[,3]
x4 = multi[,5]
plot(x3, mod1$residuals)
plot(x2, mod1$residuals)
plot(x4, mod1$residuals)
plot(mod1$fitted.values, mod1$residuals)
```
--- 

As can be seen from the plots above the residuals look iid and therefore the assumption that the residuals are i.i.d is not violated.

---
```{r}
par(mfrow=c(2,2))
plot(mod1, which = 1:4)
```
---

In the upper left plot of the residuals against the fitted values we can see that the values are centered around zero and the red line is relatively flat indicating that there is not a non-linear relationship.

In the upper right plot we can see that the normal qq plot indicates that the residuals are normally distributed or iid.

The bottom left plot shows us whether there is homoscesdasticity or equal variance of the residuals.

In the bottom right we can see whether there are outliers in the data which might influence the fit. We can remove these observations and refit the model and compare the differences.


sources:
1.) 
http://sphweb.bumc.bu.edu/otlt/MPH-Modules/BS/R/R5_Correlation-Regression/R5_Correlation-Regression7.html
2.) 
http://data.library.virginia.edu/diagnostic-plots/