
---
Title: Markdown Doc. #1

```{r}
x1 = arima.sim(model = list(ar = c(0.4,0,0)),1000)

plot.ts(x1, main = "Time Series of an Ar(1) model", ylab = "AR(1)", col = "red")
```

```{r}
x2 = arima.sim(model = list( ma= c(0,0,1)),1000)

plot.ts(x2, main = "Time Series of an MA(1) model", ylab = "MA(1)", col = "blue")
```


```{r}
x3 = arima.sim(model = list(order(1,0,1)),1000)
plot.ts(x3, main= "Time Series of and ARMA(1,1)", ylab = "ARMA(1,1)")
```

The three graphs above are: AR(1), MA(2), and an ARMA(1,0,1) processes respectively. They were generated using the arima.sim function which generates an autoregressive, moving average or auto-regressive moving average model depending on what the inputs are.

```{r}
library(fakeR)
data(co2)

co2 <- data.frame(co2)
co2$year <- c(1:nrow(co2))

CO2 <- simulate_dataset_ts(co2, cluster ="co2",time.variable = "year")

plot.ts(CO2, main = expression(paste("Time Series of CO"[2], "Data")), ylab = expression(paste("CO"[2], " in ppm")))

```


In order to use the simulate_dataset_ts function we had to first import the data, then turn it into a dataframe and then create a column called year and then feed these two variables into the function.


# add line
